Large-Scale Content-Based Matching of MIDI and Audio Files

### 2015-03-10 paper.tex
Title and authors
Abstract

\title{Paper Template For ISMIR \conferenceyear}

%\twoauthors
%  {First author} {School \\ Department}
%  {Second author} {Company \\ Address}

@@

\begin{abstract}
\end{abstract}

>>>>

\title{Large-Scale Content-Based Matching of MIDI and Audio Files}

%\twoauthors
%  {Colin Raffel} {LabROSA \\ Department of Electrical Engineering \\ Columbia University \\ New York, NY}
%  {Daniel P. W. Ellis} {LabROSA \\ Department of Electrical Engineering \\ Columbia University \\ New York, NY}

@@

\begin{abstract}
  MIDI files, when paired with corresponding audio recordings, can be used as ground truth for many music information retrieval tasks.
  We present a system which can efficiently match and align MIDI files to entries in a large corpus of audio content without using any metadata.
  The core of our approach is a neural network-based cross-modality hashing scheme which transforms acoustic feature matrices and MIDI piano rolls into sequences of vectors in a common Hamming space.
  Once represented in this way, we can efficiently perform large-scale dynamic time warping searches to match MIDI data to audio recordings.
  We evaluate our approach on the task of matching a huge corpus of MIDI files to the Million Song Dataset.
\end{abstract}
